Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
fixed wrong refference
section 6 updated

		The routing in the network is done by Onion Routers, also called relay nodes. The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in II-D). Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}. Each circuit has three type of Onion Routers \cite{mccoy2008shining}:

@@

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet). For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc. This table is available on the same Github page. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained. This Github project, including the table, is publicly available.

>>>>

		The routing in the network is done by Onion Routers, also called relay nodes. The relay nodes relay the data from the Onion Proxy to the web server across a circuit (circuits are described in \ref{ss:tor_circuit}). Each Onion Router is connected to every other Onion Router with a TLS connection \cite{tlsprotocol}. Each circuit has three type of Onion Routers \cite{mccoy2008shining}:

@@

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of (anonymous) decentralized systems (available at https://github.com/redecentralize/alternative-internet). For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc. This table is available on the same Github page. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained. This Github project, including the table, is publicly available.
